\vspace{1.0cm} \LARGE \bf Revealing the competitive dynamics of influenza viruses through evolutionary cartography \\ or \\ Charting antigenic drift and evolutionary success of seasonal influenza lineages

### 2013-01-14 flux.tex
Include additional title possibilities.

%%% TITLE %%%
\title{\vspace{1.0cm} \LARGE \bf 
Revealing the competitive dynamics of influenza viruses through evolutionary cartography \\
or \\
Charting antigenic drift and evolutionary success of seasonal influenza lineages
}

>>>>

%%% TITLE %%%
\title{\vspace{1.0cm} \Large \bf 
Revealing the competitive dynamics of influenza viruses through evolutionary cartography \\
or \\
Charting antigenic drift and evolutionary success of seasonal influenza lineages \\
or \\
Integrating influenza antigenic dynamics with molecular evolution \\
or \\
Cartographic analysis of antigenic dynamics and evolutionary success of seasonal influenza lineages \\
or \\
Integrating antigenic cartography and molecular evolution to characterize predictors of evolutionary success of seasonal influenza lineages 
}
